Evaluating Open Information Extraction for Ontologization of a Thematic Domain

### 2014-07-15 paper/iswc-2014/rebuttals.txt

Thanks for the feedback. We believe most issues pointed out can be resolved adding slightly more details in the paper.

Common issues:

Corpus and groundtruth: The ontologies (groundtruth for concepts and relation-types) were built with the help of a renowned musicologist (Dr. N Ramanathan) and musicians (T. M. Krishna and his student Vignesh Ishwar). The concepts and relation-types used for evaluation belong to the top most level in the ontologies and are agreed upon by all. The groundtruth for entities for each concept correspond to pagetitles in the respective category from Wikipedia (eg: Carnatic_musicians).

Choice of evaluation measures: We preferred overlap and residual measures over precision and recall as there are legitimate entities recognized in the assertions that are not part of the groundtruth. For technical correctness, we chose to call it an overlap instead of precision. So is the case with residual.

Reviewer#1:

We partially use non-taxonomical relations for identifying entities and concepts in the bootstrapping approach. For ReVerb and OpenIE4.0, the multiword named entities are handled in their implementations. In the semantic parsing based system, we identify consequetive NNPs and merge them into one in a pre-processing step.

A frequency filter of 5 was arrived at by trial and error. The candidates which do not satisfy this criteria are observed to be noise with a high probability. LSA transformation with a tf-idf weighting of term vectors was used as it compares the term vectors beyond the simple term frequencies and co-occurrences.

Figures will be updated with the suggestions given, and some of them will be presented as tables. The software and the data in the github repository are being updated currently.

Reviewer#2:

issue 1 -> We agree that the Open IE systems have different methodologies and goals to that of Boxer. For an evaluation using our framework, the only requirement for the system is that its extractions should be in the form of triples. The Boxer's output is transformed appropriately. The triples (input) were then used to build and populate an ontology (output), measuring the success of the each system.

issues 2&3 -> addressed above.

issue 4 -> Please note that the systems are compared only for the task of ontologization, and not information extraction in general. The number of relation-types, concepts and entities are representative of the size of the ontology learned and the volume by which it is populated (and the frequency filter is explained above). Note that differences between relative performances in quantitative and qualitative analysis expose systems which overgenerate wrong relation-types.

Reviewer#3:

The groundtruth for relations is not constructed from the extractions (explained in common-issues above). Using a frequency filter, we choose relations from the extractions, manually map them to the relations in ontologies to evaluate them qualitatively.

Using this framework on other domains is definitely a direction we want to pursue in the near future. The license was a generic choice of the university. It can surely be changed to a more open one.

### 2014-07-15 paper/ekaw-2014/ekaw2014.tex
changes for ekaw 2014 underway

Our data consists of the plain text obtained from the Wikipedia pages corresponding to the Carnatic and Hindustani music traditions, after removing the tables, listings, figures, infoboxes and other structured content. Text from each page is tokenized to sentences, which are further filtered using the following constraints: a minimum number of 3 words and a maximum of 21 words per sentence, with each word not exceeding 30 characters in length. These constraints are empirically found to greatly reduce the number of malformed and highly complex sentences.

We observed that a majority of the sentences featured pronouns. The resulting assertions only partially contribute to ontologization. For instance, consider the sentence `She is a composer'. The resulting assertion would be (She, is a, composer). With a few more of such sentences, it is possible to learn that there exists a concept called \textit{composer}. However, such assertions are helpless in identifying entities of the corresponding concept. Therefore, the pronouns in the text from each page are resolved using the deterministic coreference resolution described in~\cite{Lee2013b}\footnote{Available online at http://nlp.stanford.edu/software/dcoref.shtml}. There were a few false assertions as a result. However, there is a substantial rise in the recall of the entities in the domain. Table.~\ref{tab:data} lists the total number of sentences, and the number of assertions extracted using the OIE systems. ReVerb and Open IE 4.0 associate a confidence score with the extracted assertions. We did not however choose to filter them based on this score, as \cite{Soderland2010} advocates that a system with a better recall at the cost of lower precision is actually preferred for knowledge-base population using open information extraction. All the assertions are converted to the triple form.
\begin{table}
 \begin{center}
 \begin{tabularx}{0.9\textwidth}{X X X X X}
 \noalign{\hrule height 1.1pt}
  \textbf{Music} & \textbf{\#Sentences} & \textbf{\#ReVerb} & \textbf{\#OpenIE 4.0} & \textbf{\#Sem. Parsing}\\
  \hline
  Carnatic  & 10284 & 9844 & 15013 & 19241 \\
  Hindustani  & 10724 & 9944 & 15777 & 18496 \\
 \noalign{\hrule height 1.1pt}
 \end{tabularx}
\end{center}
\caption{The number of sentences for each music, and the number of extractions obtained from the OIE systems.} 
\label{tab:data}
\end{table}

\section{Evaluation framework}
\label{sec:framework}
In the information extraction literature, different approaches are evaluated by measuring their performances on a set of labelled sentences or by employing human judges~\cite{Fader2011a,Mausam2012a}. Our goal, however, is to evaluate them by the usefulness of the assertions extracted. We quantify this using a series of tasks that help in understanding the coverage of the entities and the relation types of a given domain in the extracted assertions, quantitatively and qualitatively.  The tasks discussed in the first part of the evaluation compare the volume of the assertions. While in the second part, we validate to what extent the assertions yield to be structured. We then juxtapose and compare the results from both parts of the evaluation.

@@

\subsection{Qualitative assessment}
The tasks discussed in this section are complementary to those presented in the former, validating whether the quantitative observations correlate with the performances of OIE systems on various tasks in ontologization. For this, we consider the three fundamental tasks of ontologization: entity identification, concept identification and semantic relation extraction~\cite{Petasis2011}.

\subsubsection{Concept identification.} It is the task of identifying the concepts in the domain. Objects from all the triples featuring a subsumption relation phrase are collected. They are disambiguated based on their spellings, mostly automatically using string matching and edit distance measures\footnote{Available at https://github.com/gopalkoduri/string-matching} with minimal manual intervention where necessary. The resulting objects are taken to be the candidate concepts of the given domain. We compare the coverage of these against the concepts\footnote{The term concept is used analogous to the term class in ontologies.} in the ontologies\footnote{Available at https://github.com/gopalkoduri/ontologies} manually engineered with the help of music experts, for each of the Carnatic and Hindustani music.

@@

For evaluating the first subtask of entity identification, i.e., finding the entities of the given domain, we measure the overlapping ($O$) and the residual ($R$) portions of the candidate entities from each system with respect to the reference set. If $X$ is the set of candidate entities and $Y$ is the reference set, $O$ and $R$ are defined as:
\begin{eqnarray}
\label{eq:overlap}
O(X, Y) = \frac{\left|X \cap Y \right|}{\left|Y\right|} \\\nonumber
R(X, Y) = \frac{\left|X - Y \right|}{\left|X\right|}
\end{eqnarray}

@@

\subsubsection{Semantic relation extraction.} It refers to the relation types other than those which convey concept hierarchies. The assertion shown in Fig.~\ref{fig:ccg_sample} is one such example, where \textit{plays} is a relation that connects \textit{person} and \textit{musical instrument} concepts. We compare the OIE systems in this task by two measures: breadth and depth of the identified relation types. Breadth corresponds to the absolute number of valid relation types identified for each concept, and the depth corresponds to the number of assertions for a given relation type that consist of the identified entities. The valid relation types are manually marked from among the relation phrases in the assertions with a frequency constraint of 5 assertions per relation phrase.
\afterpage{
\begin{figure}[t]
\begin{center}
        \subfigure[][Sentences]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/quantitative/carnatic_music/extrations-per-sentence.pdf}
		 \label{fig:quant-carnatic-sentences}
        }% 
        \qquad
        \subfigure[][Objects]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/quantitative/carnatic_music/extrations-per-argument.pdf}
		 \label{fig:quant-carnatic-object}
        }%
        \\
        \subfigure[][Relation types]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/quantitative/carnatic_music/extrations-per-reltype.pdf}
		 \label{fig:quant-carnatic-reltype}
        }% 
        \qquad
        \subfigure[][Concepts]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/quantitative/carnatic_music/extrations-per-class.pdf}
		 \label{fig:quant-carnatic-concept}
        }% 
\end{center}
\caption{Distribution of no. of extractions from OIE systems for Carnatic music shown along different \textit{aspects}. For a given number of extractions on x-axis, the y-axis shows the logarithmic count of the instances in the \textit{aspect}, which have at least those many extractions.}
\label{fig:quant-carnatic}
\end{figure}
}

\afterpage{
\begin{figure}[t]
\begin{center} 
        \subfigure[][Sentences]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/quantitative/hindustani_music/extrations-per-sentence.pdf}
		 \label{fig:quant-hindustani-sentences}
        }%
        \qquad
        \subfigure[][Objects]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/quantitative/hindustani_music/extrations-per-argument.pdf}
		 \label{fig:quant-hindustani-object}
        }%
        \\
        \subfigure[][Relation types]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/quantitative/hindustani_music/extrations-per-reltype.pdf}
		 \label{fig:quant-hindustani-reltype}
		}%
        \qquad
        \subfigure[][Concepts]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/quantitative/hindustani_music/extrations-per-class.pdf}
		 \label{fig:quant-hindustani-concept}
        }%
\end{center}
\caption{Distribution of no. of extractions from OIE systems for Hindustani music shown along different \textit{aspects}. For a given number of extractions on x-axis, the y-axis shows the logarithmic count of the instances in the \textit{aspect}, which have at least those many extractions.}
\label{fig:quant-hindustani}
\end{figure}
}

@@

%\afterpage{
\begin{figure}[t!]
\begin{center}
        \subfigure[][Overlap with reference data.]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/entity-identification/rule-based/carnatic_music/class-agreement-with-wikipedia.pdf}
		 \label{fig:qual-object-rulebased-carnatic-wikipedia}
        }% 
        \qquad
        \subfigure[][Inter-system agreement for residual entity cadidates.]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/entity-identification/rule-based/carnatic_music/class-agreement-inter-method.pdf}
		 \label{fig:qual-object-rulebased-carnatic-inter}
		}%
		\\
        \subfigure[][Overlap with reference data.]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/entity-identification/rule-based/hindustani_music/class-agreement-with-wikipedia.pdf}
		 \label{fig:qual-object-rulebased-hindustani-wikipedia}
        }%
        \qquad
        \subfigure[][Inter-system agreement for residual entity cadidates.]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/entity-identification/rule-based/hindustani_music/class-agreement-inter-method.pdf}
		 \label{fig:qual-object-rulebased-hindustani-inter}
        }%
\end{center}
\caption{Results for rule-based concept assignment of entities identified in Carnatic (top) and Hindustani (bottom) music.}
\label{fig:qual-object-rulebased}
\end{figure}
%}

@@

\afterpage{
\begin{figure}[p]
\begin{center}
        \subfigure[][Musicians]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/entity-identification/bootstrapping/carnatic_music/carnatic_musicians.pdf}
		 \label{fig:qual-object-bootstrapping-carnatic-musicians}
        }% 
        \qquad
        \subfigure[][Composers]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/entity-identification/bootstrapping/carnatic_music/carnatic_composers.pdf}
		 \label{fig:qual-object-bootstrapping-carnatic-composers}
        }%
        \\
        \subfigure[][Instrumentalists]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/entity-identification/bootstrapping/carnatic_music/carnatic_instrumentalists.pdf}
		 \label{fig:qual-object-bootstrapping-carnatic-instrumentalists}
        }% 
        \qquad
        \subfigure[][Singers]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/entity-identification/bootstrapping/carnatic_music/carnatic_singers.pdf}
		 \label{fig:qual-object-bootstrapping-carnatic-singers}
        }%
        \\
        \subfigure[][Ragas]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/entity-identification/bootstrapping/carnatic_music/carnatic_ragas.pdf}
		 \label{fig:qual-object-bootstrapping-carnatic-ragas}
        }% 
        \qquad
        \subfigure[][Compositions]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/entity-identification/bootstrapping/carnatic_music/carnatic_compositions.pdf}
		 \label{fig:qual-object-bootstrapping-carnatic-compositions}
        }%
\end{center}
\caption{Results for bootstrapping-based concept assignment of entities identified in Carnatic music}
\label{fig:qual-object-bootstrapping-carnatic}
\end{figure}
\clearpage
}
\afterpage{
\begin{figure}[t]
\begin{center}
        \subfigure[][Musicians]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/entity-identification/bootstrapping/hindustani_music/hindustani_musicians.pdf}
		 \label{fig:qual-object-bootstrapping-hindustani-musicians}
        }% 
        \qquad
        \subfigure[][Ragas]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/entity-identification/bootstrapping/hindustani_music/hindustani_ragas.pdf}
		 \label{fig:qual-object-bootstrapping-hindustani-ragas}
        }% 
%        \subfigure[][Composers]{%
%		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/entity-identification/bootstrapping/hindustani_music/hindustani_composers.pdf}
%		 \label{fig:qual-object-bootstrapping-hindustani-composers}
%        }%
        \\
        \subfigure[][Instrumentalists]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/entity-identification/bootstrapping/hindustani_music/hindustani_instrumentalists.pdf}
		 \label{fig:qual-object-bootstrapping-hindustani-instrumentalists}
        }% 
        \qquad
        \subfigure[][Singers]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/entity-identification/bootstrapping/hindustani_music/hindustani_singers.pdf}
		 \label{fig:qual-object-bootstrapping-hindustani-singers}
        }%
%        \\
\end{center}
\caption{Results for bootstrapping-based concept assignment of entities identified in Hindustani music. The results for hindustani composers were not included due to space constraints.}
\label{fig:qual-object-bootstrapping-hindustani}
\end{figure}
%\clearpage
}

@@

The second method for the evaluation of concept assignment employs bootstrapping as discussed in sec.~\ref{sec:framework}. This process involves selection of a seedset and determining the number of bootstrapping iterations. For the sake of brevity, we have set the size of seedset to be the same for all the concepts, which is 3. The entities in the seedset are randomly chosen from the ones among the reference data taken from Wikipedia. However, as the bootstrapping process itself can be sensitive to the initial selection of the entities in the seedset, the whole process is repeated 5 times with randomly chosen seedsets. The bootstrapping method is terminated once the size of seedset reaches that of the corresponding concept in the reference data. After every 5 instances added during the process, we measure the overlap ($O$) and residual ($R$) portions of the seedset with respect to the reference data.  Figs.~\ref{fig:qual-object-bootstrapping-carnatic} and \ref{fig:qual-object-bootstrapping-hindustani} show their mean over 5 runs. 
\afterpage{
\begin{figure}[!t]
\begin{center}
        \subfigure[][Carnatic music: No. of valid relation types]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/semantic-relation-extraction/carnatic_music.pdf}
		 \label{fig:qual-semantic-relex-carnatic}
        }% 
        \qquad
        \subfigure[][Carnatic music: No. of corresponding assertions]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/semantic-relation-extraction/carnatic_music-relcount.pdf}
		 \label{fig:qual-semantic-relex-carnatic-relcount}
        }%
        \\
        \subfigure[][Hindustani music: No. of valid relation types]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/semantic-relation-extraction/hindustani_music.pdf}
		 \label{fig:qual-semantic-relex-hindustani}
        }%
        \qquad
        \subfigure[][Hindustani music: No. of corresponding assertions]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/semantic-relation-extraction/hindustani_music-relcount.pdf}
		 \label{fig:qual-semantic-relex-hindustani-relcount}
        }%
\end{center}
\caption{Semantic relation extraction task: The number of valid relation types marked for each concept, and the number of corresponding assertions that include the entities in the domain.}
\label{fig:qual-semantic-relex}
\end{figure}
}

>>>>

\subsection{Text corpus}
Our data consists of the plain text obtained from the Wikipedia pages corresponding to the Carnatic and Hindustani music traditions, after removing the tables, listings, figures, infoboxes and other structured content. Pages from the parent categories corresponding to both music traditions are obtained recursively. Text from each page is tokenized to sentences, which are further filtered using the following constraints: a minimum number of 3 words and a maximum of 21 words per sentence, with each word not exceeding 30 characters in length. These constraints are empirically found to reduce the number of malformed and highly complex sentences.

We observed that a majority of the sentences featured pronouns. The resulting assertions only partially contribute to ontologization. For instance, consider the sentence `She is a composer'. The resulting assertion would be (She, is a, composer). A few such sentences might help us learn that there exists a concept called \textit{composer}. However, such assertions are helpless in identifying entities of the corresponding concept. Therefore, the pronouns in the text from each page are resolved using the deterministic coreference resolution described in~\cite{Lee2013b}\footnote{Available online at http://nlp.stanford.edu/software/dcoref.shtml}. There were a few false assertions as a result. However, there is a substantial rise in the recall of the entities in the domain. Table.~\ref{tab:data} lists the total number of sentences, and the number of assertions extracted using the OIE systems. ReVerb and Open IE 4.0 associate a confidence score with the extracted assertions. We did not however choose to filter them based on this score, as \cite{Soderland2010} advocates that a system with a better recall at the cost of lower precision is actually preferred for knowledge-base population using open information extraction. All the assertions are converted to the triple form.
\begin{table}
 \begin{center}
 \begin{tabularx}{0.9\textwidth}{X X X X X}
 \noalign{\hrule height 1.1pt}
  \textbf{Music} & \textbf{\#Sentences} & \textbf{\#ReVerb} & \textbf{\#OpenIE 4.0} & \textbf{\#Sem. Parsing}\\
  \hline
  Carnatic  & 10284 & 9844 & 15013 & 19241 \\
  Hindustani  & 10724 & 9944 & 15777 & 18496 \\
 \noalign{\hrule height 1.1pt}
 \end{tabularx}
\end{center}
\caption{The number of sentences for each music, and the number of extractions obtained from the OIE systems.} 
\label{tab:data}
\end{table}

\subsection{Gold standard}
We use the ontologies manually engineered with the help of domain experts (one musicologist and three musicians) as groundtruth for the evaluation in the tasks of concept identification and semantic relation extraction\footnote{Available at https://github.com/gopalkoduri/ontologies}. The concepts and relation-types used in our evaluation framework belong to the top most level in the ontologies and are agreed upon by all the experts. The groundtruth for entities for each concept correspond to the page-titles in the respective subcategory in the Wikipedia (eg: Carnatic\_musicians).

\section{Evaluation framework}
\label{sec:framework}
%TODO clear specification of what requirement a system should fullfill to allow for meaningful comparison within the proposed framework.

In the information extraction literature, different approaches are evaluated by measuring their performances on a set of labeled sentences or by employing human judges~\cite{Fader2011a,Mausam2012a}. Our goal, however, is to evaluate them by the usefulness of the assertions extracted. We quantify this using a series of tasks that help in understanding the coverage of the entities and the relation types of a given domain in the extracted assertions, quantitatively and qualitatively. The tasks discussed in the first part of the evaluation compare the volume of the assertions. While in the second part, we validate to what extent the assertions yield to be structured. We then juxtapose and compare the results from both parts of the evaluation.

@@

\subsection{Qualitative assessment}
Though the number of relation-types, concepts and entities are representative of the size of the ontology learned and the volume by which it is populated, the numbers alone might be misleading as not all the extractions from a given system are unique and meaningful. The differences between relative performances in quantitative and qualitative analysis expose those systems which overgenerate wrong/redundant relation-types.

Consequently, the tasks discussed in this section are complementary to those presented in the former, validating whether the quantitative observations correlate with the performances of OIE systems on various tasks in ontologization. For this, we consider the three fundamental tasks of ontologization: entity identification, concept identification and semantic relation extraction~\cite{Petasis2011}.

%TODO how did you deal with multi-word expressions like names? Did your parser provide you with multiword named entities?

%filtering everything below a frequency of 5, or using LSA vectors, are less clear.

%Tables instead of figures where relevant

\subsubsection{Concept identification.} It is the task of identifying the concepts in the domain. Objects from all the triples featuring a subsumption relation phrase are collected. They are disambiguated based on their spellings, mostly automatically using string matching and edit distance measures\footnote{Available at https://github.com/gopalkoduri/string-matching} with minimal manual intervention where necessary. The resulting objects are taken to be the candidate concepts of the given domain. We compare the coverage of these against the concepts\footnote{The term concept is used analogous to the term class in ontologies.} in the manually built ontologies.

@@

For evaluating the first subtask of entity identification, i.e., finding the entities of the given domain, we measure the overlapping ($O$) and the residual ($R$) portions of the candidate entities from each system with respect to the reference set. If $X$ is the set of candidate entities and $Y$ is the reference set, $O$ and $R$ are defined as:
\begin{eqnarray}
\label{eq:overlap}
O(X, Y) = \frac{\left|X \cap Y \right|}{\left|Y\right|} \\\nonumber
R(X, Y) = \frac{\left|X - Y \right|}{\left|X\right|}
\end{eqnarray}
The overlap and residual measures are preferred to other standard measures such as precision and recall as there are legitimate entities recognized in the assertions that are not part of the groundtruth. For technical correctness, we chose to evaluate using custom measures that convey the same information.

@@

\subsubsection{Semantic relation extraction.} It refers to the relation types other than those which convey concept hierarchies. The assertion shown in Fig.~\ref{fig:ccg_sample} is one such example, where \textit{plays} is a relation that connects \textit{person} and \textit{musical instrument} concepts. We compare the OIE systems in this task by two measures: breadth and depth of the identified relation types. Breadth corresponds to the absolute number of valid relation types identified for each concept, and the depth corresponds to the number of assertions for a given relation type that consist of the identified entities. The valid relation types are manually marked from among the relation phrases in the assertions with a frequency constraint of 5 assertions per relation phrase.
\afterpage{
\begin{figure}[t]
\begin{center}
        \subfigure[][Sentences]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/quantitative/carnatic_music/extrations-per-sentence.pdf}
		 \label{fig:quant-carnatic-sentences}
        }% 
        \qquad
        \subfigure[][Objects]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/quantitative/carnatic_music/extrations-per-argument.pdf}
		 \label{fig:quant-carnatic-object}
        }%
        \\
        \subfigure[][Relation types]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/quantitative/carnatic_music/extrations-per-reltype.pdf}
		 \label{fig:quant-carnatic-reltype}
        }% 
        \qquad
        \subfigure[][Concepts]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/quantitative/carnatic_music/extrations-per-class.pdf}
		 \label{fig:quant-carnatic-concept}
        }% 
\end{center}
\caption{Distribution of no. of extractions from OIE systems for Carnatic music shown along different \textit{aspects}. For a given number of extractions on x-axis, the y-axis shows the logarithmic count of the instances in the \textit{aspect}, which have at least those many extractions.}
\label{fig:quant-carnatic}
\end{figure}
}

\afterpage{
\begin{figure}[t]
\begin{center} 
        \subfigure[][Sentences]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/quantitative/hindustani_music/extrations-per-sentence.pdf}
		 \label{fig:quant-hindustani-sentences}
        }%
        \qquad
        \subfigure[][Objects]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/quantitative/hindustani_music/extrations-per-argument.pdf}
		 \label{fig:quant-hindustani-object}
        }%
        \\
        \subfigure[][Relation types]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/quantitative/hindustani_music/extrations-per-reltype.pdf}
		 \label{fig:quant-hindustani-reltype}
		}%
        \qquad
        \subfigure[][Concepts]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/quantitative/hindustani_music/extrations-per-class.pdf}
		 \label{fig:quant-hindustani-concept}
        }%
\end{center}
\caption{Distribution of no. of extractions from OIE systems for Hindustani music shown along different \textit{aspects}. For a given number of extractions on x-axis, the y-axis shows the logarithmic count of the instances in the \textit{aspect}, which have at least those many extractions.}
\label{fig:quant-hindustani}
\end{figure}
}

@@

%\afterpage{
\begin{figure}[t!]
\begin{center}
        \subfigure[][Overlap with reference data.]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/qualitative/entity-identification/rule-based/carnatic_music/class-agreement-with-wikipedia.pdf}
		 \label{fig:qual-object-rulebased-carnatic-wikipedia}
        }% 
        \qquad
        \subfigure[][Inter-system agreement for residual entity cadidates.]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/qualitative/entity-identification/rule-based/carnatic_music/class-agreement-inter-method.pdf}
		 \label{fig:qual-object-rulebased-carnatic-inter}
		}%
		\\
        \subfigure[][Overlap with reference data.]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/qualitative/entity-identification/rule-based/hindustani_music/class-agreement-with-wikipedia.pdf}
		 \label{fig:qual-object-rulebased-hindustani-wikipedia}
        }%
        \qquad
        \subfigure[][Inter-system agreement for residual entity cadidates.]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/qualitative/entity-identification/rule-based/hindustani_music/class-agreement-inter-method.pdf}
		 \label{fig:qual-object-rulebased-hindustani-inter}
        }%
\end{center}
\caption{Results for rule-based concept assignment of entities identified in Carnatic (top) and Hindustani (bottom) music.}
\label{fig:qual-object-rulebased}
\end{figure}
%}

@@

\afterpage{
\begin{figure}[p]
\begin{center}
        \subfigure[][Musicians]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/qualitative/entity-identification/bootstrapping/carnatic_music/carnatic_musicians.pdf}
		 \label{fig:qual-object-bootstrapping-carnatic-musicians}
        }% 
        \qquad
        \subfigure[][Composers]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/qualitative/entity-identification/bootstrapping/carnatic_music/carnatic_composers.pdf}
		 \label{fig:qual-object-bootstrapping-carnatic-composers}
        }%
        \\
        \subfigure[][Instrumentalists]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/qualitative/entity-identification/bootstrapping/carnatic_music/carnatic_instrumentalists.pdf}
		 \label{fig:qual-object-bootstrapping-carnatic-instrumentalists}
        }% 
        \qquad
        \subfigure[][Singers]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/qualitative/entity-identification/bootstrapping/carnatic_music/carnatic_singers.pdf}
		 \label{fig:qual-object-bootstrapping-carnatic-singers}
        }%
        \\
        \subfigure[][Ragas]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/qualitative/entity-identification/bootstrapping/carnatic_music/carnatic_ragas.pdf}
		 \label{fig:qual-object-bootstrapping-carnatic-ragas}
        }% 
        \qquad
        \subfigure[][Compositions]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/qualitative/entity-identification/bootstrapping/carnatic_music/carnatic_compositions.pdf}
		 \label{fig:qual-object-bootstrapping-carnatic-compositions}
        }%
\end{center}
\caption{Results for bootstrapping-based concept assignment of entities identified in Carnatic music}
\label{fig:qual-object-bootstrapping-carnatic}
\end{figure}
\clearpage
}
\afterpage{
\begin{figure}[t]
\begin{center}
        \subfigure[][Musicians]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/qualitative/entity-identification/bootstrapping/hindustani_music/hindustani_musicians.pdf}
		 \label{fig:qual-object-bootstrapping-hindustani-musicians}
        }% 
        \qquad
        \subfigure[][Ragas]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/qualitative/entity-identification/bootstrapping/hindustani_music/hindustani_ragas.pdf}
		 \label{fig:qual-object-bootstrapping-hindustani-ragas}
        }% 
%        \subfigure[][Composers]{%
%		 \includegraphics[width=0.45\linewidth]{../../data/results/qualitative/entity-identification/bootstrapping/hindustani_music/hindustani_composers.pdf}
%		 \label{fig:qual-object-bootstrapping-hindustani-composers}
%        }%
        \\
        \subfigure[][Instrumentalists]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/qualitative/entity-identification/bootstrapping/hindustani_music/hindustani_instrumentalists.pdf}
		 \label{fig:qual-object-bootstrapping-hindustani-instrumentalists}
        }% 
        \qquad
        \subfigure[][Singers]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/qualitative/entity-identification/bootstrapping/hindustani_music/hindustani_singers.pdf}
		 \label{fig:qual-object-bootstrapping-hindustani-singers}
        }%
%        \\
\end{center}
\caption{Results for bootstrapping-based concept assignment of entities identified in Hindustani music. The results for hindustani composers were not included due to space constraints.}
\label{fig:qual-object-bootstrapping-hindustani}
\end{figure}
%\clearpage
}

@@

The second method for the evaluation of concept assignment employs bootstrapping as discussed in sec.~\ref{sec:framework}. This process involves selection of a seedset and determining the number of bootstrapping iterations. For the sake of brevity, we have set the size of seedset to be the same for all the concepts, which is 3. The entities in the seedset are randomly chosen from the ones among the reference data taken from Wikipedia. However, as the bootstrapping process itself can be sensitive to the initial selection of the entities in the seedset, the whole process is repeated 5 times with randomly chosen seedsets. The bootstrapping method is terminated once the size of seedset reaches that of the corresponding concept in the reference data. After every 5 instances added during the process, we measure the overlap ($O$) and residual ($R$) portions of the seedset with respect to the reference data.  Figs.~\ref{fig:qual-object-bootstrapping-carnatic} and \ref{fig:qual-object-bootstrapping-hindustani} show their mean over 5 runs. 
\afterpage{
\begin{figure}[!t]
\begin{center}
        \subfigure[][Carnatic music: No. of valid relation types]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/qualitative/semantic-relation-extraction/carnatic_music.pdf}
		 \label{fig:qual-semantic-relex-carnatic}
        }% 
        \qquad
        \subfigure[][Carnatic music: No. of corresponding assertions]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/qualitative/semantic-relation-extraction/carnatic_music-relcount.pdf}
		 \label{fig:qual-semantic-relex-carnatic-relcount}
        }%
        \\
        \subfigure[][Hindustani music: No. of valid relation types]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/qualitative/semantic-relation-extraction/hindustani_music.pdf}
		 \label{fig:qual-semantic-relex-hindustani}
        }%
        \qquad
        \subfigure[][Hindustani music: No. of corresponding assertions]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/qualitative/semantic-relation-extraction/hindustani_music-relcount.pdf}
		 \label{fig:qual-semantic-relex-hindustani-relcount}
        }%
\end{center}
\caption{Semantic relation extraction task: The number of valid relation types marked for each concept, and the number of corresponding assertions that include the entities in the domain.}
\label{fig:qual-semantic-relex}
\end{figure}
}
